%TODO: add new publication -done 
%TODO: get tech report number for first publication 

% TODO:  add  HadoopJitter
%reference entry' to list of publications = %TODO: find HadoopJitter
%reference entry'  + TODO: format it below

%TODO: discuss acceptance rate 
%TODO: add publisher name, e.g., ACM

%TODO: consider splitting into short and long articles 

%\textbf{\underline{Long Articles}}\\

\underline{Papers}
\begin{enumerate} 
\item Mathialakan Thavappiragasasm and Vivek Kale. \textbf{\textit{CPU-GPU Performance Tuning for Improving Performance of Modern Scientific Applications on Exascale Supercomputers}}. IEEE HiPC 2023. Goa, India. December 18-21, 2023.
\item Shravan Kale, Kevin Huck, David Boehme, Vanessa Surjadidjaja and Vivek Kale. \textbf{\textit{Performance Analysis and Auto-tuning Tools for Performance Portable Parallel Programs}}. 2023 ACM/IEEE International Conference for High Performance Computing Networking, Storage, and Analysis. Denver, CO, USA. November 12-17, 2023.

\item Vivek Kale, Vanessa Surjadidjaja, Christian Trott and James Brandt. \textbf{\textit{Data Order Reduction for Performance Monitoring of Supercomputers via the Kokkos Tools Sampler Utility}} LDMSCon 2023. Boston, MA, USA. June 13-15, 2023. 

\item Vivek Kale and Shyamali Mukherjee. \textbf{\textit{Tools to Rapidly Develop Sophisticated HPC Software Libraries}} SIAM Computational Science and Engineering Conference 2023. Amsterdam, Netherlands. March 2, 2023.

\item Mathialakan Thavappiragasam and Vivek Kale. \textbf{\textit{OpenMP’s Asynchronous Offloading for All-pairs Shortest Path Graph Algorithms on GPUs}}  HiPar 2022 Workshop at The 2022 ACM/IEEE International Conference for High Performance Computing Networking, Storage, and Analysis. November 16, 2022. Dallas, Texas, USA. 

\item Mathialakan Thavappiragasam, Vivek Kale, Oscar Hernandez and  Ada Sedova. \textbf{\textit{Addressing Load Imbalance in Bioinformatics and Biomedical Applications: Efficient Scheduling across Multiple GPUs}} In Proceedings of 12th International Workshop on High Performance Bioinformatics and Biomedicine. December 9, 2021. Houston, Texas, USA. 

\item Barbara Chapman, Buu Pham, Charlene Yang, Christopher Daley, Colleen Bertoni, Dhruva Kulkarni, Dhruva Kulkarni, Dossay Oryspayev, Ed D’Azevedo, Helen He, Johannes Doerfert, Keren Zhou, Kiran Ravikumar, Mark Gordon, Mauro Del Ben, Meifeng Lin, Melisa Alkan, Michael Kruse, Oscar Hernandez, P. K. Yeung, Paul Lin, Peng Xu, Swaroop Pophale, Tosaporn Sattasathuchana, Vivek Kale, William Huhn and Dhruva Kulkarni. \textbf{\textit{Outcomes of OpenMP Hackathon: OpenMP Application Experiences with the Offloading Model: Part 1}} In Proceedings of 17th International Workshop on OpenMP, IWOMP 2021, Bristol, UK, September 14–16, 2021. 

\item Barbara Chapman, Buu Pham, Charlene Yang, Christopher Daley, Colleen Bertoni, Dhruva Kulkarni, Dhruva Kulkarni, Dossay Oryspayev, Ed D’Azevedo, Helen He, Johannes Doerfert, Keren Zhou, Kiran Ravikumar, Mark Gordon, Mauro Del Ben, Meifeng Lin, Melisa Alkan, Michael Kruse, Oscar Hernandez, P. K. Yeung, Paul Lin, Peng Xu, Swaroop Pophale, Tosaporn Sattasathuchana, Vivek Kale, William Huhn and Dhruva Kulkarni. \textbf{\textit{Outcomes of OpenMP Hackathon: OpenMP Application Experiences with the Offloading Model: Part 2}} In Proceedings of 17th International Workshop on OpenMP, IWOMP 2021, Bristol, UK, September 14–16, 2021. 

\item Seonmyeong Bak, Colleen Bertoni, Swen Boehm, Reuben Budiardja, Barbara M. Chapman, Johannes Doerfert, Markus Eisenbach, Hal Finkel, Oscar Hernandez, Joseph Huber, Shintaro Iwasaki, Vivek Kale, Paul R.C. Kent, JaeHyuk Kwack, Meifeng Lin, Piotr Luszczek, Ye Luo, Buu Pham and P.K. Yeung. \textbf{\textit{OpenMP Application Experiences: Porting to Accelerated Nodes}}.  In Journal of Parallel Computing. October 23rd, 2021.

\item Vivek Kale, Wenbin Lu, Anthony Curtis, Abid Malik, Barbara Chapman and Oscar Hernandez. \textbf{\textbf{Toward Supporting MultiGPU targets via taskloop and User-defined Schedules}}. Proceedings of the 2020 International Workshop of OpenMP. September 23-25, 2020. Austin, USA. (virtual) 

\item Jonas H Müller Korndörfer, Florina M. Ciorba, Akan Yilmaz, Christian Iwainsky, Johannes Doerfert, Hal Finkel, Vivek Kale, Michael Klemm. \textbf{\textit{A Runtime Approach for Dynamic Load Balancing of OpenMP Parallel Loops in LLVM}}. The International Conference for High Performance Computing Networking, Storage, and Analysis. November 19, 2019. Denver, Colorado, USA.

\item Vivek Kale, Christian Iwainsky, Michael Klemm, Jonas H. Muller Korndorfer, Florina M. Ciorba. \textbf{\textit{Toward a Standard Interface for User-Defined Scheduling in OpenMP}}. International Workshop on OpenMP. September 23, 2019. Auckland, New Zealand. 
\item Vivek Kale and William D. Gropp. \textbf{\textit{Composing Low-Overhead Scheduling Strategies for Improving Performance of Scientific Applications}}. IWOMP 2015. October 2015. Aachen, Germany.
\item Simplice Donfack, Vivek Kale, Laura Grigori and William D. Gropp. \textbf{\textit{Hybrid Static/Dynamic Scheduling for Already Optimized Dense Matrix Factorizations}}. IPDPS 2012. May 2012. Shanghai, China.
\item Vivek Kale, Abhinav Bhatele and William D. Gropp. \textbf{\textit{Weighted Locality-sensitive Scheduling for
      Noise Mitigation on Multicore Clusters}}. HiPC 2011. December
  2011. Bangalore, India. 
\item Vivek Kale and William D. Gropp. \textbf{\textit{Load Balancing for Regular Meshes on a Cluster of SMPs with MPI}}. EuroMPI 2010. September 2010. Stuttgart, Germany. \textit{\textcolor{red}{(Selected as a Best Paper)}}
\item Torsten Hoefler, James Dinan, Darius Buntinas, Pavan Balaji, Brian Barrett, Ron Brightwell, William Gropp, Vivek Kale and Rajeev Thakur. \textbf{\textit{MPI+MPI: A New Hybrid Approach to Parallel Programming with MPI Plus Shared Memory}}. EuroMPI 2012. September 2012. Madrid, Spain.
\item Amanda Randles, Vivek Kale, Jeff Hammond, William D. Gropp and Efthimios Kaxiras. \textbf{\textit{Performance Analysis of the Lattice
Boltzmann Model Beyond Navier-Stokes}}. IPDPS 2013. May 2013. Boston, USA.
\item Vivek Kale. \textbf{\textit{Towards Using and Improving the NAS Parallel Benchmarks: A Parallel Patterns Approach}}. ParaPLoP 2010. April 2010. Carefree, USA.
\item Vivek Kale and Edgar Solomonik. \textbf{\textit{Parallel Sorting Pattern}}. ParaPLoP 2010. April 2010. Carefree, USA. 
\item Vivek Kale. \textbf{\textit{The Correlation between Parallel Patterns and the NAS Parallel Benchmarks}}. ICSE 2010. May 2010. Johannesberg, South Africa.
\end{enumerate} 

\underline{Extended Abstracts}
\begin{enumerate}
\item Vivek Kale and Martin Kong. \textbf{\textit{Enhancing Support in OpenMP to Improve Data Locality in Application Programs Using Task Scheduling}}. OpenMPCon 2018. September 2018. Barcelona, Spain.
\item Vivek Kale and William D. Gropp. \textbf{\textit{A User-defined Schedule for OpenMP}}. Extended Abstract. OpenMPCon
  2017. September 2017. New York, USA.
\item Vivek Kale. \textbf{\textit{A Pattern Language for Dynamic Scheduling}}. ParaPLoP 2011. May 2011. Carefree, USA.
\end{enumerate}

\underline{Posters}
\begin{enumerate}
\item Raul Torres, Vivek Kale, Abid Malik, Tom Scogland, Roger Ferrer and Barbara M. Chapman. \textbf{\textit{Support in OpenMP for Multi-GPU Parallelism}}. The International Conference for High Performance Computing Networking, Storage, and Analysis. November 19, 2021. St. Louis, Missouri, USA.
\item Vivek Kale and Oscar Hernandez. {\bf\textit{Performance Portability of User-defined Loop Schedules}}. DOE PPP 2019. April 2019. Denver, USA.
\item Vivek Kale, Harshitha Menon and Karthik Senthil. \textbf{\textit{Adaptive Loop Scheduling with Charm++ to Improve Performance of Scientific Applications}}. SC 2017. November 2017. Denver, USA. \textit{\textcolor{red}{(Selected as a Candidate for Best Poster)}}
\item Vivek Kale, Simplice Donfack, Laura Grigori and William D. Gropp. \textbf{\textit{Balancing the Tradeoff Between Load Balancing and Locality to Improve Performance of Scientific Applications}}. SC 2014. November 2014. New Orleans, USA.
\item Vivek Kale, Amanda Randles and William D. Gropp. \textbf{\textit{Locality-Optimized Mixed Static/Dynamic
      Scheduling for Load Balancing on SMPs}}. EuroMPI/ASIA 2014. September 2014. Kyoto, Japan.
\end{enumerate}

%TODO: add HadoopJitter here 

%\item Vivek Kale. \textbf{\textit{Enabling Simulation of Renewable
%    Energy Solutions through Supercomputers}}. Technical Report
%  2009. TR0210-373. May 2009. University of Illinois at Urbana-Champaign.

%\end{enumerate} 
