\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\begin{center}
    \Large \textbf{Vivek L. Kale} \\
    \normalsize
    \vspace{0.2cm}
    \href{mailto:vivek.lkale@gmail.com}{vivek.lkale@gmail.com} | 
    \href{http://vlkale.github.io}{http://vlkale.github.io} | 
    \href{http://www.linkedin.com/in/vlkale}{http://www.linkedin.com/in/vlkale}\\
    US Citizen with Secret Clearance
\end{center}

\vspace{0.5cm}
\noindent\rule{\linewidth}{0.4pt}
 \fontfamily{lmss}\selectfont
\section*{Professional Summary}
Highly skilled computational scientist and software developer with expertise in high-performance computing (HPC), runtime systems, and parallel programming models. Proven track record in designing scalable solutions for Exascale systems, contributing to OpenMP standards, and developing performance tools for scientific computing applications. Effective communicator and collaborative team player with a strong publication record and extensive technical expertise.

\section*{Professional Experience}

\textbf{Sandia National Laboratories}\\
\textit{Principal Member of Technical Staff II} \hfill \textit{July 2024 - Present}\\
\textit{Senior Member of Technical Staff} \hfill \textit{August 2022 - July 2024}
\begin{itemize}[noitemsep,topsep=0pt]
\item Owner of HPC Tools and Runtime Systems, serving as the primary liaison for LLNL Performance Tools and Kokkos Tools maintainer.
\item Contributed to OpenMP specification and MPI forum as Sandia Representative, enhancing the scalability and usability of parallel programming standards.
\item Spearheaded initiatives to improve runtime efficiency and performance of HPC applications, collaborating with multidisciplinary teams.
\end{itemize}

\textbf{Brookhaven National Laboratory}\\
\textit{Computational Scientist} \hfill \textit{May 2019 - August 2022}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Designed and implemented OpenMP user-defined multiGPU scheduling in LLVM to enhance within-node load balancing for AI and scientific workloads, achieving improved resource utilization.
    \item Developed benchmarks and conducted performance evaluations on Exascale supercomputers, including Frontier and Aurora.
    \item Represented Brookhaven National Laboratory on the OpenMP Architecture Review Board, contributing to the evolution of HPC standards.
\end{itemize}

\textbf{Charmworks, Inc.}\\
\textit{Software Developer} \hfill \textit{June 2018 - April 2019}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Conducted research and development for User-defined Loop Schedules (UDS) in OpenMP, enabling custom scheduling strategies for diverse workloads.
    \item Integrated OpenMP UDS loop scheduling into Charm++\textquotesingle s CkLoop, streamlining workflow and optimizing performance for complex applications.
\end{itemize}

\section*{Education}
\textbf{Ph.D., Computer Science} \hfill \textit{University of Illinois at Urbana-Champaign, 2015}\\
Dissertation: \textit{\textquotedbl Optimized Runtime Systems for High-Performance Scientific Computing\textquotedbl}

\textbf{B.S., Computer Science} \hfill \textit{University of Illinois at Urbana-Champaign, 2007}

\section*{Publications}
\begin{enumerate}[noitemsep,topsep=0pt]
    \item Vivek Kale, Hanru Yan, Shyamali Mukherjee, et al. \textit{Toward Automated Detection of Portability Bugs in Kokkos Parallel Programs.} SC24 Correctness Workshop, November 2024, Atlanta, USA.
    \item Vivek Kale, Wenbin Lu, Anthony Curtis, et al. \textit{Toward Supporting Multi-gpu Targets via Taskloop and User-defined Schedules.} IWOMP 2020, September 2020 (Virtual).
    \item Simplice Donfack, Vivek Kale, Laura Grigori, William D. Gropp. \textit{Hybrid Static/Dynamic Scheduling for Already Optimized Dense Matrix Factorizations.} IPDPS 2012, May 2012, Shanghai, China.
\end{enumerate}

\section*{Technical Skills}
\textbf{Programming Languages:} C, C++, Python, CUDA, Fortran, Bash, Csh, VHDL, Matlab, Java\\
\textbf{Libraries and Frameworks:} OpenMP (gomp, llvm), Kokkos, HIP, POSIX Threads (Pthreads), MPI (mpich), OpenACC (pgi), Globus Toolkit\\
\textbf{Tools and Utilities:} Kokkos Tools, PMPI, OMPT, NVIDIA Nsight, Tau, HPCToolkit, Intel VTune, Clang-Tidy, KLEE, Gprof, GDB, Docker, Git, CMake, Spack, Clang-Format, GNUplot, Emacs, Autoconf, LaTeX

\section*{Projects}
\begin{itemize}[noitemsep,topsep=0pt]
    \item \textbf{LLVM\textquotesingle s OpenMP:} Enhanced LLVM OpenMP runtime with user-defined schedules and multiGPU support. \\Repository:\href{https://github.com/sollve/openmp-rts}{https://github.com/sollve/openmp-rts}
    \item \textbf{Kokkos/C++ Tools:} Developed and maintained runtime systems and tools for Kokkos. \\Repository: \href{https://github.com/kokkos/kokkos-tools}{https://github.com/kokkos/kokkos-tools}
\end{itemize}

\section*{Additional Information}
\begin{itemize}[noitemsep,topsep=0pt]
    \item  Obtained Certificate from UCLA Technical Management Program in September 2024
\end{itemize}

\end{document}
